Finite element analysis ofmulti-dimensional and simplifiedmodels for beams and plates

### 2023-10-07 files/Chapter6/Validity_Plate.tex
summary

\begin{figure}[H]
    \centering
    \begin{adjustbox}{center}
        \includegraphics[scale=0.7]{Convergence.png}
    \end{adjustbox}
    \caption{Rate of convergence of the first 20 eigenvalues.}
    \label{fig:conv_3d_eig}
\end{figure}
\textcolor{red}{Update this figure.}

@@

>>>>

\begin{figure}[H]
    \centering
    \begin{adjustbox}{center}
        \includegraphics[scale=0.4]{Plate accuracy_no_legend.png}
    \end{adjustbox}
    \caption{Rate of convergence of the first 20 eigenvalues.}
    \label{fig:conv_3d_eig}
\end{figure}

@@

\FloatBarrier
\begin{table}[htbp]
	\scalebox{.8}{
	\makebox[\textwidth]{
		\caption{Comparison of eigenvalues with $b = 1.75$, with decreasing values of $h$.}
		\begin{tabular}{|cccc||cccc||cccc||cccc|}
			\hline
			\multicolumn{16}{|c|}{Comparison of Eigenvalues, $b = 1.75$} \\
			\hline\hline
			\multicolumn{4}{|c||}{$h = 1/5$}       & \multicolumn{4}{c||}{$h =1/10$}      & \multicolumn{4}{c||}{$h = 1/20$}      & \multicolumn{4}{c|}{$h = 1/30$} \\
			\hline
			{i} & {3D} & {j} & {Plate} & {i} & {3D} & {j} & {Plate} & {i} & {3D} & {j} & {Plate} & {i} & {3D} & {j} & {Plate} \\
			\hline
			1 & 0.13062 & 1 & 0.12939 & 1 & 0.034245 & 1 & 0.034079 & 1 & 0.0086697 & 1 & 0.32670086456 & 1 & 0.0038626 & 1 & 0.0038541\\
			2 & 0.32016 & 2 & 0.31779 & 2 & 0.089872 & 2 & 0.089508 & 2 & 0.023395 & 2 & 0.023323 & 2 & 0.010507 & 2 & 0.010475\\
			3 & 1.2496 & 3 & 1.2422 & 3 & 0.36964 & 3 & 0.36841 & 3 & 0.098072 & 3 & 0.097745 & 3 & 0.044239 & 3 & 0.044074\\
			4 & 1.9808 &  & - & 4 & 1.2274 & 4 & 1.2188 & 4 & 0.33233 & 4 & 0.33118 & 4 & 0.15003 & 4 & 0.14964\\
			5 & 3.7675 & 4 & 3.7086 & 5 & 1.352 & 5 & 1.3465 & 5 & 0.36764 & 5 & 0.36652 & 5 & 0.16657 & 5 & 0.16605\\
			6 & 4.2021 & 5 & 4.1631 & 6 & 1.6994 & 6 & 1.6894 & 6 & 0.4647 & 6 & 0.4632 & 6 & 0.21059 & 6 & 0.21002\\
			7 & 5.2022 & 6 & 5.1381 & 7 & 1.9763 &  & - & 7 & 0.79935 & 7 & 0.79606 & 7 & 0.3656 & 7 & 0.36423\\
			8 & 7.6603 & 7 & 7.9399 & 8 & 2.8259 & 7 & 2.8076 & 8 & 1.2445 & 8 & 1.2411 & 8 & 0.56685 & 8 & 0.56529\\
			9 & 8.0445 &  & - & 9 & 4.4507 & 8 & 4.4294 & 9 & 1.5708 & 9 & 1.563 & 9 & 0.72384 & 9 & 0.72032\\
			10 & 9.0791 &  & - & 10 & 5.3923 & 9 & 5.3539 & 10 & 1.9739 &  & - & 10 & 1.1585 & 10 & 1.1545\\
			11 & 10.135 &  & - & 11 & 7.6371 &  & 0 & 11 & 2.5137 & 10 & 2.5015 & 11 & 1.2513 & 11 & 1.2466\\
			12 & 12.888 & 8 & 12.736 & 12 & 8.4707 & 10 & 8.3817 & 12 & 2.708 & 11 & 2.6947 & 12 & 1.4005 & 12 & 1.3927\\
			13 & 14.506 & 9 & 14.302 & 13 & 9.0612 & 11 & 8.9704 & 13 & 3.0153 & 12 & 2.9984 & 13 & 1.4449 & 13 & 1.4393\\
			14 & 14.892 &  & - & 14 & 9.0682 & 12 & 9.9347 & 14 & 3.137 & 13 & 3.1246 & 14 & 1.6806 & 14 & 1.6738\\
			15 & 19.395 &  & - & 15 & 10.018 & 13 & 10.605 & 15 & 3.6118 & 14 & 3.5928 & 15 & 1.973 &  & -\\
			16 & 21.265 & 10 & 20.79 & 16 & 10.131 &  & - & 16 & 5.1287 & 15 & 5.0977 & 16 & 2.4081 & 15 & 2.3958\\
			17 & 22.512 & 11 & 22.038 & 17 & 10.683 &  & - & 17 & 5.6368 & 16 & 5.6009 & 17 & 2.6419 & 16 & 2.6253\\
			18 & 25.193 & 12 & 24.775 & 18 & 11.806 & 14 & 11.682 & 18 & 6.5069 & 17 & 6.4687 & 18 & 3.0386 & 17 & 3.0189\\
			19 & 27.783 & 13 & 27.322 & 19 & 14.893 &  & - & 19 & 7.6243 & 18 & 7.6617 & 19 & 3.6563 & 18 & 3.6342\\
			20 & 28.461 & 14 & 27.851 & 20 & 16.275 & 15 & 16.1 & 20 & 7.7152 &  & - & 20 & 4.3466 & 19 & 4.3267\\
			\hline
			\multicolumn{2}{|c}{Max RE:} & \multicolumn{2}{c||}{3.6499\%} & \multicolumn{2}{c}{Max RE:} & \multicolumn{2}{c||}{9.5565\%} & \multicolumn{2}{c}{Max RE:} & \multicolumn{2}{c||}{0.63674\%} & \multicolumn{2}{c}{Max RE:} & \multicolumn{2}{c|}{0.64798\%} \\
			\hline
		\end{tabular}
		\label{tab:Table_plate_3}
	}}
\end{table}
\FloatBarrier

Table \ref{tab:Table_plate_3} that for a wide plate with $b=1.75$, the models do compare very well. However it seems like the height of the plate does no longer have a significant effect on the accuracy of the eigenvalues. What can be seen is that as het height decreases, the number of plate type eigenvalues within the first 20 eigenvalues increases quite significant.

### 2023-10-07 files/Overview.tex
summary

\subsubsection{Chapter 3}
\subsubsection{Chapter 4}
\subsubsection{Chapter 5}
\subsubsection{Chapter 6}

>>>>

\subsubsection{Chapter 3}
In this chapter, some theory for the Finite Element Method is discussed. This chapter contains two parts, that covers two different results. The first result is the convergence of the Galerkin approximation of a general vibration problem. This result is presented in the article \cite{BV13}. The second result concerns the convergence of the eigenvalues and eigenfunctions of a one-dimensional vibration problem when applying the Finite Element Method. This result is presented in the textbook \cite{SF97}. In the first section, the authors continue with the general vibration problem that is used in chapter 2. The general vibration problem has a solution as shown in chapter 2. The Galerkin Approximation is derived from the general vibration probelm and is rewritten into a system of ordinary differential using the Finite Element Method. This oridinary differential equation can be proven to have a unique solution. The main results of \cite{BV13} shows that this solution of the Galerkin Approximation converges to the solution of the general vibration problem. The approach of the authors is to calculate the error estimates. The error is split into two parts, a semi-discrete and a fully discrete problem. Two assumptions are added to the assumptions from chapter 2. Using these assumptions, the authors obtain error estimates for the semi-discrete and fully discrete problems.

The second part of the chapter considers work done in a textbook \cite{SF97}.

\subsubsection{Chapter 4}
\subsubsection{Chapter 5}
\subsubsection{Chapter 6}
